Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-04-27 main.tex
Added source to generate figures for bicycle model analysis.

\begin{figure}
  \centering
  \subcaptionbox{Uncontrolled root locus of eigenvalue components plotted versus speed.}{
    \includegraphics[width=70mm]{example-image-a}
  }
  \subcaptionbox{Controlled root locus of eigenvalue components plotted versus speed.}{
    \includegraphics[width=70mm]{example-image-b}
  }
  \label{fig:eigenvalues}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics{figures/balance-assist-controllers-eig-vs-speeds.png}
  \caption{Uncontrolled and controlled root locus of eigenvalue components
    plotted versus speed.}
  \label{fig:eigenvalues}
\end{figure}
